\vspace{0.15em}
\noindent\textbf{\sffamily Principal Software Engineer, AI/ML Platform} \hfill \textit{Aug 2022 -- Present} \\
\noindent{\sffamily Autodesk} \hfill \textit{San Francisco, CA | Remote}
\vspace{0.05em}

\begin{itemize}[leftmargin=1.25em, topsep=1pt, partopsep=1.5pt]
\setlength\itemsep{0.22em}

\item \textbf{Inference Backend Enablement:}
    \begin{itemize}[leftmargin=2.25em]
        \setlength\itemsep{0.2em}
        \item \textbf{Unified inference gateway:} Drove delivery of the \textbf{Go} proxy layer for the platform's unified inference gateway, unifying \textbf{AWS SageMaker}, \textbf{Bedrock}, and custom endpoints and integrating with \textbf{AuthN/AuthZ} to expose a single gateway for all inference backends.
        \item \textbf{Async inference at scale:} Shipped \textbf{async inference} support behind the proxy layer, enabling larger payloads and longer runtimes and unlocking use cases such as \textbf{video processing} and long-running model inference.
        \item \textbf{Batch inference and cost optimization:} Established the \textbf{SageMaker Batch Transform} workflow and upstream compute integration, reducing per-unit inference cost and standardizing batch ML pipelines across teams.
    \end{itemize}
\vspace{0.4em}

\item \textbf{Enterprise Feature Store Platform:}
    \begin{itemize}[leftmargin=2.25em]
        \setlength\itemsep{0.2em}
        \item \textbf{Feature Store \& governance:} Led design and delivery of Autodesk's first \textbf{centralized Feature Store} on \textbf{AWS SageMaker}, codifying feature publishing, access controls, and cross-team reuse. Shipped a \textbf{Python SDK} for feature discovery and retrieval across online and batch inference.
        \item \textbf{Batch \& streaming:} Engineered automated publishing across \textbf{batch} (\textbf{Spark}, \textbf{Ray}) and \textbf{streaming} (\textbf{Flink}, \textbf{Kafka}) pipelines.
        \item \textbf{Compliance:} Implemented \textbf{GDPR-compliant retention \& deletion} workflow with \textbf{Spark} and \textbf{Airflow}, meeting regulatory obligations at enterprise scale.
        \item \textbf{Multi-tenant access:} Defined \textbf{FastAPI}-based service layer for feature group lifecycle and access provisioning, with per-tenant encryption and fine-grained access control.
        \item \textbf{LLM readiness:} Extended the architecture with \textbf{OpenSearch}-based Vector DB and \textbf{Vector Data Lake}, enabling unified management of structured features and embeddings.
    \end{itemize}
\vspace{0.4em}

\item \textbf{Unified Labeling Platform:}
    \begin{itemize}[leftmargin=2.25em]
        \setlength\itemsep{0.2em}
        \item \textbf{Enterprise adoption in 6 weeks:} Delivered a production-ready \textbf{MVP in 6 weeks}, achieving enterprise-wide adoption and winning a \textbf{company-wide platform excellence award}.
        \item \textbf{Secure multi-tenant foundations:} Founded and led Autodesk's first \textbf{multi-tenant labeling platform} on \textbf{AWS SageMaker GroundTruth}, provisioned with \textbf{Terraform} for secure and scalable operations.
        \item \textbf{Annotation throughput:} Integrated \textbf{Autodesk Viewer} into labeling workflows, supporting proprietary data formats and speeding up annotation pipelines.
        \item \textbf{Event-driven data flow:} Designed \textbf{post-annotation workflows} with \textbf{event-driven architecture}, ensuring version control and seamless delivery of labeled data into the Feature Store.
        \item \textbf{Human-in-the-loop at scale:} Championed roadmap to integrate \textbf{Active Learning} and \textbf{Amazon Augmented AI (A2I)} for model-assisted annotation and human-in-the-loop validation.
    \end{itemize}
\vspace{0.4em}

\item \textbf{Platform Architecture \& Leadership:}
    \begin{itemize}[leftmargin=2.25em]
        \setlength\itemsep{0.2em}
        \item \textbf{Hiring and team building:} Functioned as \textbf{hiring manager} for AI/ML Data Systems—partnered with \textbf{HR} to define role requirements, lead candidate evaluation, and build a high-performing team.
        \item \textbf{Data Mesh ML environment:} Architected a decentralized \textbf{SageMaker Studio ML environment} based on \textbf{Data Mesh} principles, enabling distributed compute with centralized governance for hundreds of tenants.
        \item \textbf{IaC \& self-service:} Developed security-hardened \textbf{Terraform modules} for \textbf{EMR} and \textbf{EKS}, enabling compliant deployments of \textbf{Airflow}, \textbf{Ray}, and \textbf{Spark}. Built \textbf{AWS Service Catalog} integration for on-demand \textbf{Spark clusters} with \textbf{CloudFormation}.
        \item \textbf{Data contracts \& catalog:} Standardized ingestion via data contracts, raising catalog consistency and data quality for AI/ML in the central lake.
    \end{itemize}

\end{itemize}
