\vspace{0.3em}
\noindent\textbf{\sffamily Principal Software Engineer, AI/ML Data Systems} \hfill \textit{Aug 2022 -- Present} \\
\noindent{\sffamily Autodesk} \hfill \textit{San Francisco, CA | Remote}
\vspace{0.1em}

\begin{itemize}[leftmargin=*, topsep=2pt, partopsep=2.5pt]
\setlength\itemsep{0.3em}

\item \textbf{Enterprise Feature Store Platform:}
    \begin{itemize}[leftmargin=1.5em]
        \setlength\itemsep{0.3em}
        \item \textbf{Standardized feature reuse and governance:} Architected Autodesk’s first \textbf{centralized Feature Store} on \textbf{AWS SageMaker}, codifying feature publishing, access controls, and cross-team reuse.
        \item \textbf{Scaled batch and streaming:} Engineered automated publishing across \textbf{batch} (\textbf{Spark}, \textbf{Ray}) and \textbf{streaming} (\textbf{Flink}, \textbf{Kafka}) pipelines.
        \item \textbf{Accelerated training and serving integration:} Shipped a \textbf{Python SDK} that unifies feature discovery and retrieval across online and batch inference, reducing integration effort and time-to-production for ML teams.
        \item \textbf{Ensured compliance:} Implemented a \textbf{GDPR-compliant retention \& deletion} workflow with \textbf{Spark} and \textbf{Airflow}, meeting regulatory obligations at enterprise scale.
        \item \textbf{Hardened multi-tenant access:} Defined a \textbf{FastAPI-based service layer} for feature group lifecycle and access provisioning, with per-tenant encryption and fine-grained access control.
        \item \textbf{Enabled LLM readiness:} Extended the architecture with an \textbf{OpenSearch-based Vector DB} and \textbf{Vector Data Lake}, enabling unified management of structured features and embeddings.
    \end{itemize}

\item \textbf{Unified Labeling Platform:}
    \begin{itemize}[leftmargin=1.5em]
        \setlength\itemsep{0.3em}
        \item \textbf{Enterprise adoption in 6 weeks:} Delivered a production-ready \textbf{MVP in 6 weeks}, achieving enterprise-wide adoption and winning a \textbf{company-wide platform excellence award}.
        \item \textbf{Secure multi-tenant foundations:} Founded and led Autodesk’s first \textbf{multi-tenant labeling platform} on \textbf{AWS SageMaker GroundTruth}, provisioned with \textbf{Terraform} for secure and scalable operations.
        \item \textbf{Faster annotation throughput:} Integrated \textbf{Autodesk Viewer} into labeling workflows, supporting proprietary data formats and speeding up annotation pipelines.
        \item \textbf{Versioned, event-driven data flow:} Designed \textbf{post-annotation workflows} with \textbf{event-driven architecture}, ensuring version control and seamless delivery of labeled data into the Feature Store.
        \item \textbf{Human-in-the-loop at scale:} Championed roadmap to integrate \textbf{Active Learning} and \textbf{Amazon Augmented AI (A2I)} for model-assisted annotation and human-in-the-loop validation.
    \end{itemize}

\item \textbf{Platform Architecture \& Leadership:}
    \begin{itemize}[leftmargin=1.5em]
        \setlength\itemsep{0.3em}
        \item \textbf{Governed ML environments at scale:} Architected a decentralized \textbf{SageMaker Studio ML environment} based on \textbf{Data Mesh} principles, enabling distributed compute with centralized governance for hundreds of tenants.
        \item \textbf{Compliance by design:} Developed security-hardened \textbf{Terraform modules} for \textbf{EMR} and \textbf{EKS}, enabling compliant deployments of \textbf{Airflow}, \textbf{Ray}, and \textbf{Spark}.
        \item \textbf{Self-service analytics:} Built \textbf{AWS Service Catalog} integration for on-demand \textbf{Spark clusters} with \textbf{CloudFormation}, enabling self-service analytics at enterprise scale.
        \item \textbf{Data contracts and catalog standards:} Standardized ingestion via data contracts, raising catalog consistency and data quality for AI/ML in the central lake.
        \item \textbf{Team building:} Functioned as \textbf{hiring manager}, partnering with \textbf{HR} to define role requirements, lead candidate evaluation, and build a high-performing AI/ML Data Systems team.
    \end{itemize}

\item \textbf{Selected Impact:}
    \begin{itemize}[leftmargin=1.5em]
        \setlength\itemsep{0.3em}
        \item Enterprise-wide adoption of Feature Store and Labeling Platform; accelerated feature reuse and time-to-production across teams.
        % Optionally populate with concrete figures, e.g., "X+ teams, Y+ feature groups, Z TB/day, P95 < L ms, N% TTM reduction".
    \end{itemize}

\end{itemize}