{\raggedright\normalsize
\textbf{VP, Big Data Platform Architect} {\hfill\footnotesize\textsc{| 01/15/2018 -- Present}}\\ 
\textbf{TD Securities} {\hfill\footnotesize\textsc{| New York, NY}}}
\setlength\vspace{0pt}

\begin{flushleft}
Architected Hadoop big data infrastructure used by various trading desks and internal engineering teams from the ground up.
Headed big data project and improved platform to achieve multi-tenancy, secure and highly availability. 
As big data platform product owner, my primary job function included:  
\end{flushleft}

\begin{itemize}[leftmargin=*, topsep=1pt, partopsep=2.5pt]
\setlength\itemsep{-0.2em}

\item Built Big Data Infrastructure on Premises and Cloud

\begin{itemize}[leftmargin=*, topsep=-5pt, partopsep=2.5pt]
\setlength\itemsep{-0.2em}
\item Pioneered infrastructure-as-code workflow and developed Ansible script to automatically deploy Hortonworks distribution Hadoop Big Data Platform (HDP) on premises environments.  
\item Led HDP SaltSatck script development and successfully improved efficiency to deploy complex Hadoop ecosystem (HDFS, YARN, HBASE, HIVE, SPARK, KAFKA) into diverse cloud like Azure.
\end{itemize}

\item Developed and Orchestrated Scalable ETL Pipelines

\begin{itemize}[leftmargin=*, topsep=-5pt, partopsep=2.5pt]
\setlength\itemsep{-0.2em}
\item Established Airflow cluster with Celery and RabbitMQ backend from scratch, which elevated capabilities of handling multiple ETL tasks and enhanced visibility of data management.
\item Implemented Spark based end of day market data ingestion pipeline digested from Kafka, which successfully boosted data processing time over 100\%.
\end{itemize}

\item Administered Prod and Dev Big Data Platform

\begin{itemize}[leftmargin=*, topsep=-5pt, partopsep=2.5pt]
\setlength\itemsep{-0.2em}
\item Led Hadoop administration group to maintain, upgrade platform and recover from disaster. Advised solutions for clients across New York, Toronto and London with over 50 developers tp onboard big data applications.
\item Devised code based configuration managemnet provisioning methodology integrated with CI/CD pipeline. Improved reliability of managing over 200 configuration parameters in Hadoop ecosystem across all prod and dev environment.
\end{itemize}

\end{itemize}

